Verifying Demonstrations

### 2017-08-03 intro.tex
Adds more comments
Adds limitations on methods, todo for Venezuelan protests

After many demonstrations the count by police and that by the organizers 
differ, in some instances the difference can be hundreds of thousands.
There are numerous examples, e.g.\ the demonstrations in South 
Korea~\cite{2016DemonstrationsInSeoul} or the women's marches in the 
US~\cite{2017WomensMarchesInUS}, where there is difficulty in establishing the 
actual number of participants.
The methods for counting the crowds vary.
There are some techniques using computer vision found in the research 
literature, e.g.\ by \textcite{CVCrowdCounting}.
These require images from the demonstration and provide no way to verify the 
authenticity of the count (except re-running the algorithm on one's own input 
data).
However, as is illustrated by 
\textcite{2016DemonstrationsInSeoul,2017WomensMarchesInUS}, the methods used in 
practice are manual and prone to errors.

@@

We can make one important observation about this problem that has seemingly 
been ignored in the past: it is an adversarial setting.
The protesters (organizers and participants) have an incentive to increase the 
tallied number of participants, whereas other interests might have an incentive 
to decrease the tallied number of participants, e.g.\ an authoritarian regime.
To solve this problem, we need a verifiable participation count.
In this paper, we combine the verifiability and privacy properties of 
electronic voting with location-proof systems to provide a verifiable 
participation count.

>>>>

After many demonstrations the count by police and that by the organizers 
differ, in some instances the difference can be hundreds of thousands.
There are numerous examples, e.g.\ the demonstrations in South 
Korea~\cite{2016DemonstrationsInSeoul} or the women's marches in the 
US~\cite{2017WomensMarchesInUS}, where there is difficulty in establishing the 
actual number of participants.
The methods for counting the crowds vary.
There are some techniques using computer vision found in the research 
literature, e.g.\ by \textcite{CVCrowdCounting}.
These require images from the demonstration and provide no way to verify the 
authenticity of the count (except re-running the algorithm on one's own input 
data).
However, as is illustrated by 
\textcite{2016DemonstrationsInSeoul,2017WomensMarchesInUS}, the methods used in 
practice are manual and prone to errors.
Additionally, none of these techniques can estimate the cumulative 
participation count without counting some people multiple times.

@@

% XXX Add the 2017 Venezuelan protests

We can make one important observation about this problem that has seemingly 
been ignored in the past: it is an adversarial setting.
The protesters (organizers and participants) have an incentive to increase the 
tallied number of participants, whereas other interests might have an incentive 
to decrease the tallied number of participants, e.g.\ an authoritarian regime.
(Or the other way around, an authoritarian regime wants to organize a 
pro-regime protest to demonstrate its \enquote{wide support}.)
To solve this problem, we need a verifiable participation count.
In this paper, we combine the verifiability and privacy properties of 
electronic voting with location-proof systems to provide a verifiable 
participation count.

### 2017-08-03 properties.tex

    \item A\ref{SpatiallyRelated} can be provided by \iacf{LP}.
  \end{itemize}
\end{idea}
}
\end{frame}
\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{strict partial 
  order}\footnote{%
  A relation \(\prec\) which is irreflexive, antisymmetric and transitive.
}.
If some objects in the set relate to known points in time, then the partial 
order allows to relate the data to the time of the event.
\Cref{SpatiallyRelated} binds the data spatially to the event.

@@

A demonstration is very different from voting in one sense: Alice must be 
physically present and that very presence shows her support for the cause.
In voting, on the other hand, Alice has multiple options which are not revealed
by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof to the blockchain, the proof must be 
unlinkable to Alice, yet, if Alice submits another proof, those two proofs must 
be linkable (due to eligibility verification, \cref{EligibilityVerif}).
E.g.\ Eve compromises Alice's device (and private keys).
Anyone can verify any proof.
With the inputs that Eve can extract from the published proof and the keys she 
can find on Alice's device, she should not be able to reproduce the same 
signatures on the proof.

\begin{frame}<presentation>
  \begin{question}
    How do we submit the proofs to storage?
    Voting normally uses mix-nets.
  \end{question}

  \begin{remark}
    Without anonymous submission we don't get vote pricacy, thus no receipt 
    freeness either.
  \end{remark}
\end{frame}

>>>>

    \item A\ref{SpatiallyRelated} can be provided by \iacf{LP}.
  \end{itemize}
\end{idea}
}
\end{frame}
\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partial 
  order}\footnote{%
  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
}.
If some objects in the set relate to known points in time, then the partial 
order allows to relate the data to the time of the event.
This allows us to \emph{authenticate the data temporally}.
\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
us to \emph{authenticate the data spatially}.

@@

A demonstration is very different from voting in one sense: Alice must be 
physically present and that very presence shows her support for the cause.
In voting, on the other hand, Alice has multiple options which are not revealed
by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof to the blockchain, the proof must be 
unlinkable to Alice, yet, if Alice submits another proof, those two proofs must 
be linkable (due to eligibility verification, \cref{EligibilityVerif}).
E.g.\ Eve compromises Alice's device (and private keys).
Anyone can verify any proof.
With the inputs that Eve can extract from the published proof and the keys she 
can find on Alice's device, she should not be able to reproduce the same 
signatures on the proof.
So Alice needs a long-term and a short-term credential, but she should not be 
able to create two short-term credentials to participate twice.

\begin{frame}
  \begin{question}
    How do we submit the proofs to storage?
    Voting normally uses mix-nets.
    Submit over Tor~\cite{Tor}?
  \end{question}

  \mode<presentation>{
  \begin{remark}
    Without anonymous submission we don't get vote privacy, thus no receipt 
    freeness either.
  \end{remark}
  }
\end{frame}
